---
title: "Trend Real Time Protection Analysis"
output: html_notebook
---

<br>

# Objective
The aim of the study is to identify devices that have the RTP deactivated within a period of time. We noticied that RTP gets deactivated randomly for a set of devices, and that might be due to conflicts with other Antiviruses.

The idea of this analysis is to identify devices with RTP OFF, and see if conflicts exists between different Antiviruses.



<br><br>

# Loading data

We get data from a powershell remote action running on each device and returning the Antivirus status for each of them.

A script is scheduled on a server that will gather all this data and consolidate it in a CSV file. This script is scheduled to run every 30 min.

After that, CSV files are dropped to a shared folder where we take it from for the analysis.

<br>

## Libraries
```{r echo=T,eval=T,warning=FALSE, message=FALSE}
library("tidyverse")
library("lubridate")
library("formattable")
library("magrittr")
```

<br> 

## Consolidate all CSVs
We create an empty tibble that we will fill with all data gathered from the CSV folder. We take the executiond date from the file names via a regex.
```{r echo=T,eval=F,warning=FALSE, message=FALSE}
empty <- tibble(
  a = character(),
  b = character(),
  c = double()
)

myFiles <- list.files("./data/")


for(filename in myFiles){

  temp <- read_delim(paste0("./data/",filename), delim = "\t")

  
  temp$day <- filename %>%
    str_extract("[0-9]{4}-[0-9]{2}-[0-9]{2}_[0-9]{2}h[0-9]{2}") %>%
    str_replace("_", " ") %>%
    str_replace("h", ":") %>%
    paste("00", sep = ":") %>%
    ymd_hms()
  
  
  empty <- rbind(empty, temp)
  
}
```

<br>

## Create consolidation table


```{r echo=T,eval=F,warning=FALSE, message=FALSE}
empty %>%
  na.omit() %>%
  mutate(trend_rtp_off = ifelse(grepl("Trend Micro OfficeScan Antivirus (RTP: off", all_antiviruses, fixed = T) & !grepl("Trend Micro OfficeScan Antivirus (RTP: on", all_antiviruses, fixed = T) , TRUE, FALSE),
         trend_rtp_on = ifelse(grepl("Trend Micro OfficeScan Antivirus (RTP: on", all_antiviruses, fixed = T), TRUE, FALSE),
         cylance_rtp_off = ifelse(grepl("CylancePROTECT (RTP: off", all_antiviruses, fixed = T), TRUE, FALSE),
         cylance_rtp_on = ifelse(grepl("CylancePROTECT (RTP: on", all_antiviruses, fixed = T), TRUE, FALSE),
         avast_rtp_off = ifelse(grepl("Avast Antivirus (RTP: off", all_antiviruses, fixed = T), TRUE, FALSE),
         avast_rtp_on = ifelse(grepl("Avast Antivirus (RTP: on", all_antiviruses, fixed = T), TRUE, FALSE),
         malwarebyte_rtp_off = ifelse(grepl("Avast Antivirus (RTP: off", all_antiviruses, fixed = T), TRUE, FALSE),
         malwarebyte_rtp_on = ifelse(grepl("Avast Antivirus (RTP: on", all_antiviruses, fixed = T), TRUE, FALSE),
         win_def_rtp_off = ifelse(grepl("Windows Defender Antivirus (RTP: off", all_antiviruses, fixed = T) | grepl("Windows Defender (RTP: off", all_antiviruses, fixed = T) , TRUE, FALSE),
         win_def_rtp_on = ifelse(grepl("Windows Defender Antivirus (RTP: on", all_antiviruses, fixed = T) | grepl("Windows Defender (RTP: on", all_antiviruses, fixed = T) , TRUE, FALSE),
         last_seen_from_execution = round(difftime(day,last_seen, units = "days"),0)) %>%
  arrange(-last_seen_from_execution) %>%
  filter(last_seen_from_execution <= 15) %>%
  select(name, day, trend_rtp_off, trend_rtp_on, cylance_rtp_off, cylance_rtp_on, avast_rtp_off, avast_rtp_on, malwarebyte_rtp_off, malwarebyte_rtp_on, win_def_rtp_off ,win_def_rtp_on) %>%
  inner_join(appearing, by = c("name" = "name")) %>% 
  group_by(name, appear) %>%
  mutate(trend_on = sum(trend_rtp_on),
         trend_off = sum(trend_rtp_off),
         cylance_on = sum(cylance_rtp_on),
         cylance_off = sum(cylance_rtp_off),
         avast_on = sum(avast_rtp_on),
         avast_off = sum(avast_rtp_off),
         malwarebyte_on = sum(malwarebyte_rtp_on),
         malwarebyte_off = sum(malwarebyte_rtp_off),
         win_def_on = sum(win_def_rtp_on),
         win_def_off = sum(win_def_rtp_off)) %>%
  ungroup() %>%
  group_by(name, appear) %>%
  summarise(pct_trend_on = round(max(trend_on/appear)*100,0),
            pct_trend_off = round(max(trend_off/appear)*100,0),
            pct_cylance_on = round(max(cylance_on/appear)*100,0),
            pct_cylance_off = round(max(cylance_off/appear)*100,0),
            pct_avast_on = round(max(avast_on/appear)*100,0),
            pct_avast_off = round(max(avast_off/appear)*100,0),
            pct_malwarebyte_on = round(max(malwarebyte_on/appear)*100,0),
            pct_malwarebyte_off = round(max(malwarebyte_off/appear)*100,0),
            pct_win_def_on = round(max(win_def_on/appear)*100,0),
            pct_win_def_off = round(max(win_def_off/appear)*100,0)) %T>%
  write_excel_csv("all_antiviruses_ON_OFF.csv")
```

<br>

## Load consolidated data and join 
We load the file saved previoulsy (to avoid to recalculate everthing again), and inner join device names with another table (table containing all devices and RA RTP status)


```{r echo=T,eval=F,warning=FALSE, message=FALSE}

df <- read_csv("./all_antiviruses_ON_OFF.csv")
df.all <- read_delim("./all.csv", delim = "\t")


```

<br>

## Summary table

```{r echo=T,eval=T,warning=FALSE, message=FALSE}

## Function needed to create the above table
funk <- function(x){
  if( x >= 0 & x <10){ return("0-10") }
  if( x >= 10 & x <20){ return("10-20") }
  if( x >= 20 & x <30){ return("20-30") }
  if( x >= 30 & x <40){ return("30-40") }
  if( x >= 40 & x <50){ return("40-50") }
  if( x >= 50 & x <60){ return("50-60") }
  if( x >= 60 & x <70){ return("60-70") }
  if( x >= 70 & x <80){ return("70-80") }
  if( x >= 80 & x <90){ return("80-90") }
  if( x >= 90){ return("90-100") }
}

df %>%
  mutate(trend = sapply(.$pct_trend_on, funk),
         cylance = sapply(.$pct_cylance_on, funk),
         avast = sapply(.$pct_avast_on, funk),
         malware = sapply(.$pct_malwarebyte_on, funk),
         windef = sapply(.$pct_win_def_on, funk)) %>%
  select(name, trend, cylance, malware, windef) %>%
  gather(trend, cylance, malware, windef, key=antivirus, value=number) %>%
  group_by(number, antivirus) %>%
  summarise(countn = n()) %>%
  spread(antivirus, countn) %>%
  replace(is.na(.), 0) %>%
  rename(`% of time RTP is ON` = number, `# of devices Cylance` = cylance, `# of devices MalwareByte` = malware,
         `# of devices Trend` = trend, `# of devices Windows Defender` = windef) %>%
  formattable()

```

  
